JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-01 report/paper.tex
Corrected the piapro compilation section.

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. As a result, the following scheme was used:

@@

Assuming an up-to-date system as of July 31, 2014, the following libraries were used in the first crawler:

@@

\begin{enumerate}
 \item Zach's laptop: g++ -g -std=c++0x main.cpp -o main `pkg-config libxml++-2.6 --cflags glib-2.0 --libs glib-2.0`
 \item EWS machines: g++ -g -std=gnu++0x main.cpp -o main -D\_GLIBCXX\_USE\_NANOSLEEP
\end{enumerate}

>>>>

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used:

@@

Assuming an up-to-date system as of July 31, 2014, the following libraries were used in the first crawler: (Note: the split up crawler uses a combination of these.)

@@

\begin{enumerate}
 \item Zach's laptop: g++ -g -std=c++0x main.cpp -o main `pkg-config libxml++-2.6 --cflags glib-2.0 --libs glib-2.0`
 \item EWS machines (crawl): g++ -g -std=gnu++0x main.cpp -o main -D\_GLIBCXX\_USE\_NANOSLEEP
 \item Zach's laptop (after EWS crawl): g++ -g -std=c++0x postParse.cpp -o postParse `pkg-config libxml++-2.6 --cflags glib-2.0 --libs glib-2.0`
\end{enumerate}
